---
title: "Developing Data Products - R Markdown and Leaflet Week 2"
author: "Raul Banares"
date: "07/05/2018"
output:
  html_document: default
  word_document: default
---

## Introduction

Create a web page using R Markdown that features a map created with Leaflet.

Host your webpage on either Git Hub Pages, R Pubs, or NeoCities.

Your webpage must contain the date that you created the document, and it must contain a map created with Leaflet. We would love to see you show off your creativity!


## Preparation

Install this R package:

```{r Preparation}
# install.packages("leaflet", dependencies=TRUE)
```

Load the library 

```{r Load_Library}
library(leaflet)
```


## Testing Leaflet package

```{r Test_package}
test_map <-  leaflet() %>%
  addTiles() %>%  
  addMarkers(lng=-3.6827, lat=40.4893, popup="Madrid city")
test_map
```

## Creating a Custom Map

```{r}
RealMadridIcon <- makeIcon(
  iconUrl = "https://es.m.wikipedia.org/wiki/Archivo:Escudo_real_madrid_1941b.png",
  iconWidth = 31*215/230, iconHeight = 31,
  iconAnchorX = 31*215/230/2, iconAnchorY = 16)

RealMadridLatLong <- data.frame(
  lat = c(40.4530100, 40.4240000, 40.479167),
  lng = c(-3.6882900, -3.6718400, -3.611667))

RealMadridSites <- c(
  "<a href='https://www.realmadrid.com/estadio-santiago-bernabeu'>Stadium</a>",
  "<a href='https://www.wizinkcenter.es/'>Basketball court</a>",
  "<a href='https://www.realmadrid.com/sobre-el-real-madrid/el-club/ciudad-real-madrid/instalaciones'>Ciudad Deportiva</a>"
)

RealMadridLatLong %>% 
  leaflet() %>%
  addTiles() %>%
  addMarkers(icon = RealMadridIcon, popup = RealMadridSites)
```

